---
title: "PanelMixedLogit Demonstration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Coordinate Exchange Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PanelMixedDesign)
library(DoE.base)
library(tidyverse)
library(ggplot2)
library(gt)

set.seed(458)
```

This vignette illustrates how to use the ```PanelMixedLogit``` library to evaluate the variance-covariance matrix for a design. For illustrative purposes, we will assume that we have a DCE with 3 attributes (two at 2-levels and one at 3-levels). We start by telling R how many attributes we have and how many levels each has:

```{r}
# 3 Attributes
nattr <- 3

# First two attributes at 2 levels, last attribute at 3 levels
n_level_attribute <- c(2, 2, 3)
```

For the purpose of this illustration, we will assume that we want a discrete choice experiment with 8 choice sets, each presenting two alternatives:

```{r}
# Number of choice sets
n_choice_set <- 8

# Number of alternatives in each choice set
n_alternative <- 2 
```

We start by generating a random design for this experiment using the ```DoE.base``` library:

```{r}
# Get a list of all possible alternatives
all_possible_alt <- purrr::quietly(fac.design)(nlevels=n_level_attribute, random=FALSE)$result

# Randomly select a subset of them for each choice set
design <- NULL
for (i_choice_set in 1:n_choice_set){
  # Random sampling of alternatives for this choice set
  new_choice_set <- all_possible_alt[sample(prod(n_level_attribute), n_alternative, replace=FALSE), ]
  # Add to the running list of choice sets
  design <- rbind(design, new_choice_set)
}
```

Next, we get the corresponding effects coded model matrix:

```{r}
contr=rep('contr.sum',nattr)
names(contr)=names(design)
contr=as.list(contr)
model_matrix = model.matrix(~., design, contrasts = contr)[,-1] 
```

Before we can assess the quality of this design, we need to define the effect means and variances. The following are used for illustration:

```{r}
# means
mu <- c(1.0, -0.4, -0.8, 0.3)

# variance
sig <- c(0.1, 0.3, 0.4, 0.4)
```

Now we can find the corresponding approximation to the variance-covariance matrix. Here we will use the MQL approach since it is the fastest:


```{r}
varcov_MQL <- varcov_approx_PML(model_matrix, 
                            method = "MQL",
                            n_choice_set = n_choice_set,
                            effect_means = mu, effect_vars = sig) 

varcov_MQL
```


